\section{\sc Projects}
\begin{itemize}[leftmargin=0cm, label={}]

\item {\bf Scholarfy - content-based recommendation for MEDLINE dataset}\\
{\em Recommendation system web application to search 14.3 millions publications from MEDLINE dataset} (ongoing project, see \href{http://pubmed.scholarfy.net}{pubmed.scholarfy.net})

\item {\bf Disambiguation of grant and publication datasets}\\
{\em Applying disambiguation algorithm to disambiguate institutions and authors from disparate dataset including MEDLINE, NIH and NSF grant datasets} (ongoing project, see on \href{https://github.com/titipata/grant_database}{\faGithubAlt})

\item {\bf Pubmed Parser}\\
{\em Python parser for PubMed Open-Access (OA) subset and MEDLINE XML repository} (see on \href{https://github.com/titipata/pubmed_parser}{\faGithubAlt})

\item {\bf pyglmnet}\\
{\em A python implementation of elastic-net regularized generalized linear models} (main contributor, see on \href{https://github.com/pavanramkumar/pyglmnet}{\faGithubAlt})

\item {\bf Neural Event Reconstruction and Detection via Sparsity (NERDS)}\\
{\em Matlab package implementing blind deconvolution method for neural spike recovery from calcium signal. Implemetation of algorithm invented by E. L. Dyer} (see on \href{https://github.com/KordingLab/nerds}{\faGithubAlt})

\item {\bf Optimal Control of Thrust-Vectored Hovering Rocket}\\
{\em Simulation of projection-based optimal control of non-linear system in Mathematica. This was the final project in an  Optimal Control of Nonlinear Systems class taught by Prof. Todd Murphey} (see on \href{https://github.com/titipata/me454_nonlinear_optimal_control}{\faGithubAlt})

\item {\bf Lagrangian Mechanics of Trapezoidal Box with Movable Link}\\
{\em Simulation of a complex dynamical system including impact using Lagrangian mechanics method in Mathematica. This was the final class project in Theory of Machine Dynamics taught by Prof. Todd Murphey }

\item {\bf Framework for Brain Image Segmentation using modified Fuzzy C-Means Clustering Algorithm}\\
{\em Research assistant under the supervision of Assoc. Prof. Panrasee Ritthipravat at AIM Laboratory. This project included a collaboration with Zaw Htet Aung and Tulakarn Ruangrong from the class project Intelligence Systems and Biomedical Signal Processing class project}

\item {\bf A Noise Reduction Technique for Hands-Free Telephony in a Car Environment, } \\
{\bf M-Max LMS Adaptive Algorithm in Hands-Free Telephony}\\
{\em Senior Projects at Digital Signal Processing Research Laboratory (DSPRL) under the supervision of Assoc. Prof. Nisachon Tangsangiumvisai}

\end{itemize}
